Irt plot extra

### 2022-09-19 manuscript_v2.Rmd
Introduction comments addressed

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, this agency is further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].
An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017]. Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019]
These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022]. Furthermore, building on earlier attempts [e.g. @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021]. Attached to different body parts (e.g., wrist, head on eye level, chest), these devices allow objectively measuring personal light exposure under real-world conditions and are valuable tools for field studies. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (cf. **Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging, especially for inexperienced laypeople. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light situations. These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source? And how can we simultaneously assess how people habitually interact with the received light?
We propose that these challenges can be tackled by assessing light-exposure-related behaviour. We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours concerning different light situations. Since, in many cases, humans have become their own agents regarding their exposure to light or darkness through artificial electric light, people's light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities. The final objective of changing light-dark exposure patterns to avoid or mitigate negative health consequences from unhealthy habits will not just need an assessment of the lighting properties but the active change of behaviours related to light exposure. We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change. Furthermore, people without light measurement expertise may find it easier to appraise and recall their behaviour concerning light exposure than subjectively assessing a light source’s properties.
To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (PAQ; @bossini2006sensibilita), a couple of self-report tools measuring visual light sensitivity, contain single items which probe the preference for specific light situations: "In the past month, how often did you need to wear dark glasses on cloudy days or indoors?" [@verriotto2017new]; "I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime. 
However, none of these questionnaires provides a scaleable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
To fill this gap, we here present the development process of a novel self-report tool - the “Light Exposure Behavior Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.

>>>>

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].

An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017]. Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019]. These findings have sparked a significant call for assessment and guidance regarding healthy light exposure as exemplified by a recently published set of consensus-based experts’ recommendations with specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022]. Furthermore, building on earlier attempts [e.g. @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance]. Attached to different body parts (e.g., wrist; head, at eye level; chest), these devices allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are a valuable tools for field studies.. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors. These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source? And how can we simultaneously assess how people habitually interact with the received light? We propose that these challenges can be tackled by assessing light-exposure-related behaviour. We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations. In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and artificial electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities. Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies. We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change.

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (@bossini2006sensibilita) are a couple of self-report tools measuring visual light sensitivity. They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime. However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios. To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.
